### 2023-03-13 paper/FPF-WG1.tex
Toni: added institute and last name umlauts

\begin{center}
  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
  \vspace{1.1cm}
  {\small
Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni Makela$^{4}$,
    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$, 
  }\\

@@

{\it \small
	~$^1$ UC Irvine  \\[0.1cm]
 	~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
  	~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
        ~$^4$ IPJ \\[0.1cm]
 }

>>>>

\begin{center}
  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
  \vspace{1.1cm}
  {\small
Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni M\"akel\"a$^{4}$,
    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$, 
  }\\

@@

{\it \small
    ~$^1$ UC Irvine  \\[0.1cm]
    ~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
    ~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
    ~$^4$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
 }
